### 2017-06-08 sheets/talk-6/sheet-6.tex
minor fixes

\begin{definition}{Minus-core of linear maps in vector spaces}
  Let $V, W$ be vector spaces over a field $K$. Let $s, t \from V \to W$ be linear functions.
  We define the linear function $s - t := \lambda v\in V. \; v(s) - t(s)$.
  Remember that for $g \from V \to W$ we have defined $core(g) := \set{ v \in V | g(v) = 0 }$.
  Now $core (s - t) = \set{v \in V | s(v) = t (v) }$.
\end{definition}

@@

\begin{exercise}[Pushouts\,vs.\,coproducts]
  Show that if $Z$ is initial and the pullback square
  \[ \xymatrix{
    Z \ar[r]_s \ar[d]^t & X \ar[d]_{p_1} \\
    Y \ar[r]^{p_2} & P
  } \]
  is the pullback of
  $ \xymatrix{
    X & Z \ar[l]_s \ar[r]^t & Y \\
  } $
  then $P$ is the coproduct of $X$ and $Y$.

>>>>

\begin{definition}{Minus-core of linear maps in vector spaces}
  Let $V, W$ be vector spaces over a field $K$. Let $s, t \from V \to W$ be linear functions.
  We define the linear function $s - t := \lambda v\in V. \; s(v) - t(v)$.
  Remember that for $g \from V \to W$ we have defined $core(g) := \set{ v \in V | g(v) = 0 }$.
  Now $core (s - t) = \set{v \in V | s(v) = t (v) }$.
\end{definition}

@@

\begin{exercise}[Pushouts\,vs.\,coproducts]
  Show that if $Z$ is initial and the pushout square
  \[ \xymatrix{
    Z \ar[r]_s \ar[d]^t & X \ar[d]_{p_1} \\
    Y \ar[r]^{p_2} & P
  } \]
  is the pushout of
  $ \xymatrix{
    X & Z \ar[l]_s \ar[r]^t & Y \\
  } $
  then $P$ is the coproduct of $X$ and $Y$.
